\chapter{Team Charter}\label{cp:team_charter}

\section{Meetings and Attendance}

\begin{enumerate}
    \item All members shall attend scheduled team meetings, be on time, and be prepared to discuss any action items they are responsible for.
    \item If a member is unable to attend a meeting, they shall send a message to the team (or a team lead) in a timely and appropriate manner.
    \item If a member is unable to attend a meeting, they shall contact a team lead after the meeting for a briefing and to understand any action items they may have been assigned.
    \item Members shall utilize the Outlook meeting invitation acceptance/declination feature to indicate attendance at meetings.
    \item Meeting notes, minutes, and agendas shall be captured and shared via \textbf{OneNote} for each meeting.
\end{enumerate}

\section {Engineering Process}

\begin{enumerate}
    \item Action items shall be recorded in \textbf{YouTrack} and reviewed at stand-ups.
    \item The team shall practice \textit{scrum}, an agile project management framework.
    \item The team shall follow the principles of agile project management.
    \item Tasks shall be started at least \qty{48}{\hour} before the task due date.
    \item Tasks shall be ready for review at least \qty{24}{\hour} before the task due date.
    \item Team members shall check YouTrack at least once every other day.
    \item Completed tasks shall be reviewed by the project manager, subsystem leads, or both.
    \item Tasks that do not meet the success criteria described in the task shall be moved back to in-progress for re-work. 
    \item Implementation details for a task shall be thoroughly documented.
    \item Major decisions shall be tracked in a decision log.
    \item All binary/non-text files (\textit{e.g.}, \textbf{SolidWorks} part/assembly files, CFD analysis files, pictures, \textbf{Ansys} files, \textit{etc.}) shall be stored and versioned in \textbf{Teams}/\textbf{SharePoint}.
    \begin{enumerate}
        \item Files that are subject to change shall have a version number appended to the file name that follows traditional \textit{semantic versioning}.
        \begin{enumerate}
            \item Semantic versioning: v\$\{major version\}.\$\{minor version\}.\$\{patch number\}
            \item \verb|nose_cone_v1.0.0.sldprt| — initial part
            \item \verb|nose_cone_v1.0.1.sldprt| — patch
            \item \verb|nose_cone_v1.1.0.sldprt| — minor change
            \item \verb|nose_cone_v2.0.0.sldprt| — major change
        \end{enumerate}
        \item Major or minor versions shall be documented in a versioning spreadsheet.
    \end{enumerate}
    \item All text-based files (\textit{e.g.}, scripts, \LaTeX{} documents, configuration files, \textit{etc.}) shall be stored and versioned in \textbf{GitHub}.
    \item All formal reports and presentations shall be drafted in \LaTeX.
    \item All engineering calculations shall be performed and reported with \textit{Système international d'unités} (SI).
\end{enumerate}

\section{Decision Flow}

\begin{enumerate}
    \item Work shall be distributed equally amongst the team, regardless of title.
    \item Minor decisions shall be made by the respective subsystem lead.
    \item Major decisions shall be cleared by the project manager, the subsystem leads, or both.
    \item The \textbf{Project Manager} shall be responsible for...
    \begin{enumerate}
        \item scheduling team meetings and morale events.
        \item scheduling task/assignment deadlines, assigning task priorities, and assigning tasks to subsystem teams.
        \item managing and tracking the budget.
        \item process change decisions.
        \item drafting reports.
        \item assisting with subsystem engineering.
    \end{enumerate}
    \item Subsystem \textbf{Lead Engineers} shall be responsible for...
    \begin{enumerate}
        \item overall system design and integration.
        \item ensuring requirements are satisfied.
        \item managing and tasking engineering their respective subsystem teams.
    \end{enumerate}
    \item The \textbf{CAD} subsystem team shall be responsible for...
    \begin{enumerate}
        \item CAD modeling.
        \item CAD assembly.
        \item 3D rendering.
    \end{enumerate}
    \item The \textbf{Flight Performance} subsystem team shall be responsible for...
    \begin{enumerate}
        \item control surfaces and control dynamics.
        \item flight stability.
        \item aerodynamic performance and analysis.
        \item propulsion performance and analysis.
        \item CFD analysis.
    \end{enumerate}
    \item The \textbf{Structures} subsystem team shall be responsible for...
    \begin{enumerate}
        \item weight calculations and analysis.
        \item material design.
        \item structural integrity and analysis.
        \item manufacturing.
    \end{enumerate}
\end{enumerate}

\section{General}

\begin{enumerate}
    \item All team members shall participate to the fullest extent possible in the work of the team and complete any assigned action items on time.
    \item If a team member feels they or someone else on the team is contributing more or less than they should, they shall bring this to the attention of the project manager.
    \item The team shall periodically engage in morale events.
    \item As a team, we shall review and update these norms twice a semester to ensure they are current and reflect the team's needs.
\end{enumerate}
